\documentclass[11pt]{dssg}

\input{latex_commands.tex}

\tolerance=500

\begin{document}

\title{Humans in Autonomy: Verifiable, Multi-Scale, Co-Design}

\author{Ella Atkins, Randal Burns, and Mark Campbell}

\maketitle



\input{motivation}






\input{background}



%Reference Mission - do we want this?
%
%Mission
%Identify thermal signatures/people of interest
%Detect and avoid or disable IEDs
%Pervasive human and autonomy elements
%High-altitude UAV 
%Large-area monitoring, long-range communications
%Visual/hyperspectral imagery
%Remote operators and analysts
%Group of small UAVs

%Thermal field imaging and video
%Local operators and analysts
%Ground robots:  IED detect and disarm
%Humans deploy and operate locally
%Intelligence collection and dissemination
%Humans:  direct observation; hand-carried devices (e.g., cell phones)
%Manned vehicles (onboard sensors/ computers/comms)
%Remote analysts/data centers

\input{research}

\input{implications}



\section*{Acknowledgements}

This think piece, and our experiences with the DSSG program in general, were enriched by many, and we would like to acknowledge them here. In particular, visits to LANL (including the Data Science at Scale Team), NRL, Army/Marine facilities, and DARPA led us to consider this as a possible topic and helped us frame the key issues. The use and adoption of technology, as well as the openness of our researchers and troops to their use were clear at many of these stops. Rebecca Grier, Frank Moses, Shelley Cazares at IDA contributed suggestions, references, and thoughtful dialogue on our topic, making our think piece much stronger. A visit to Palantir near the end of our DSSG sessions provided a nice glimpse at how a company has worked with the DoD to enable the adoption of new software and technology to support analysts. We would like to thank Raja Parasuraman (GWU), Scott Galster (AFLR/HE), and Hadas Kress-Gazit (Cornell), each of whom conduct research in related fields (human factors, formal methods), for their patience in answering questions, support with references and ideas, and interesting dialogue on our topic. 

Importantly, we would like to thank the mentors and our DSSG colleagues for making the DSSG experience a truly remarkable one for us at this point in our careers. The discussions about DSSG, DoD and life in general as we made our way around the country were amazing. The mentors have shown us that we can be in awe of them not only for their past service, but their continued selflessness in giving back to this type of program. While we will miss our DSSG colleagues, we know that we have dinner plans any time we travel to your university. We look forward to keeping in touch. 

Finally, we would like to thank Bob Robert and Katie Gliwa. Bob for his started the DSSG program, and coming back to run it now with the enthusiasm of a new DSSG member. And Katie for her remarkable professionalism, organization and wit. 


\newpage
\bibliographystyle{ieeetr}
\bibliography{dssg-refs,dssg-refs-mcadd}
\normalsize



\end{document}
